---
title: "Hello Blog in R"
author: "Ross Gilmour"
date: 2020-05-28T21:13:14-05:00
categories: ["R"]
tags: ["R Markdown", "Rmd", "knitr"]
output: 
   html_document:
     keep_tex: true
header-includes:
   - \usepackage{caption}
   - \usepackage{booktabs}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.clean = FALSE)
```

## Fit the model

```{r cars}
lmfit <- lm(mpg ~ wt, mtcars)
lmfit
```

## Cleanup model output and format table

Use \texttt{broom}'s \texttt{tidy} function to create a data frame of the model output and output that dataframe using \texttt{knitr}'s \texttt{kable} function: 

```{r output}
library(broom)        # tidyr
library(magrittr)     # %>%

library(knitr)        # kable
library(kableExtra)   # kable_styling
tidy(lmfit) %>% kable(format="latex",booktabs=TRUE,
                      caption="My table caption",digits=2) %>% 
                kable_styling(latex_options = "HOLD_position")
```
\raggedright Add \texttt{longtable} to \texttt{kable} as required. For example: \par\texttt{kable(longtable=TRUE, format="latex", booktabs=TRUE, caption="My table caption")}
